The DAO Hack

### 2019-01-09 paper/paper.tex
added _
changed gas

The split function contains a function called withdrawRewardFor which calls rewardAccount.payOut which in turn calls \textunderscore recipient.call.value. This last call to recipient.call.value is a call to the wallet of the attacker comparable to an synchronous api call. As it doesn't include any kind of gas the attacker can do whatever he desires, including recursively call the split dao function. The call.value function is used to transfer token to an address by calling a function on that address. In code the withdrawRewardFor and payOut look like this: \cite{deconstructingDaoAttack}

>>>>

The split function contains a function called withdrawRewardFor which calls rewardAccount.payOut which in turn calls \textunderscore recipient.call.value. This last call to \textunderscore recipient.call.value is a call to the wallet of the attacker comparable to an synchronous api call. As it doesn't include any kind of limitations the attacker can do whatever he desires, including recursively call the split dao function. The call.value function is used to transfer token to an address by calling a function on that address. In code the withdrawRewardFor and payOut look like this: \cite{deconstructingDaoAttack}
